### 2022-11-14 NSF2022/Description/broaderimpacts.tex
starting braoder impacts

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation and fast and accurate computational techniques that account
for important and complex systems in
soft matter.  These complex systems include
optimal shape design in metamaterials and fusion and fission of amphiphilic
bilayer membranes. The models describing colloidal systems could be
transformative in biomedicine and material science.
The research draws from
expertise in scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and offers
insight into fundamentals of material science. The project brings socially
consequential research into the classroom and offers 
undergraduates the opportunity to train alongside faculty and graduate students.
With its combination of mathematical modeling, analysis, and scientific computing,
the project highlights the importance of mathematics and computation to all areas
of science and engineering.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences,
the proposal supports two undergraduate researchers (URs) per year
from the lead institution.
PI Ryham has worked side-by-side and
published with undergraduate coauthors in
\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}.
He is presently mentoring a Clare Boothe Luce Scholar 
on mathematical analysis of trends in election redistricting.
With another Fordham supported UR,
he is finishing a paper on a closed-form 
energy density for translationally invariant bilayers. 
Based on these experiences, we have outlined three projects for the present proposal.
\begin{enumerate}[noitemsep,topsep=0pt]
%\noitemsep
\item Translate project code from MATLAB into a compiled language

@@

\item Mathematically investigate self-assembly in the zero-screen-length limit

\end{enumerate}
The UR support is for eight summer weeks. 
In addition to collaborating with the PI,
they will have tutorials and receive training in
mathematical writing and presentation.
The URs will have desks and meeting room
in a recently completed collaboration space
built for the Mathematics Department. 
As a condition of support, 
they will be required to write a summary report and
give a presentation in the university's undergraduate
research symposium.  The PI 
will encourage the
URs to participate in a national conference.

>>>>

\section{Broader Impacts}
\label{sec:BroaderImpacts}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and
offers insight into fundamentals of self-organization and collective
dynamics. The project brings socially consequential research into the
classroom and offers undergraduates the opportunity to train alongside
faculty and graduate students. With its combination of mathematical
modeling, analysis, and scientific computing, the project highlights the
importance of mathematics and computation to all areas of science and
engineering.

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
To foster training in mathematical sciences, the proposal supports two
undergraduate researchers (URs) per year at Fordham University. PI Ryham
has worked side-by-side and published with undergraduate
coauthors~\cite{RYHAM20112929, RyWaCo13, RyKlYaCo16}. He is presently
mentoring a Clare Boothe Luce Scholar on mathematical analysis of trends
in election redistricting. With another Fordham supported UR, he is
finishing a paper on a closed-form energy density for translationally
invariant bilayers. Based on these experiences, we have outlined three
projects for the present proposal.
\todo[inline]{Rolf: Can you update this?}
\begin{enumerate}[noitemsep,topsep=0pt]
\item Translate project code from MATLAB into a compiled language

@@

\item Mathematically investigate self-assembly in the zero-screen-length limit
\end{enumerate}
The UR support is for eight summer weeks. In addition to collaborating
with the PI, they will have tutorials and receive training in
mathematical writing and presentation. The URs will have desks and
meeting room in a recently completed collaboration space built for the
Mathematics Department. As a condition of support, they will be required
to write a summary report and give a presentation in the university's
undergraduate research symposium. The PI will encourage the URs to
participate in a national conference.
